### 2021-02-17 text/draft.tex
histogram

Next the so parsed single keywords must be cleaned or normalized: we
want the keywords to follow a uniform format thereby joining
morphological duplicates such as ``Gene,'' ``gene,'' " gene``,''/gene``.
Also, some keywords are in fact keyword chains, for
example''Dendrites/metabolism/ultrastructure". Keyword chains must be
broken into their component keywords and then parsed again. The reason
for this is that Annif only assigns flat keywords and not keyword
chains.

@@

>>>>

Next the so parsed single keywords must be cleaned or normalized: we
want the keywords to follow a uniform format thereby joining
morphological duplicates such as ``Gene,'' ``gene,'' ``gene\_,''
``gene/,'' and so on. Also, some keywords are in fact keyword chains,
for example ``Dendrites/metabolism/ultrastructure.'' Keyword chains must
be broken into their component keywords and then parsed again. The
reason for this is that Annif only assigns flat keywords and not keyword
chains.

@@

!! Cumulative sum histogram

\begin{figure}
\centering
\includegraphics{images/keywords_clean_histogram_a.pdf}
\caption{Bla.}
\end{figure}

\begin{figure}
\centering
\includegraphics{images/keywords_clean_histogram_b.pdf}
\caption{Bla.}
\end{figure}
